Hyperopt-Sklearn: Subtitle?

### 2014-04-26 papers/2014-automl/paper.tex
fixing bolding that disappeared somehow

\begin{table}
  \begin{threeparttable}
    \caption{
        Hyperopt-sklearn scores relative to selections from literature on the three data sets used in our experiments.
        On MNIST, hyperopt-sklearn is one of the best-scoring methods that does not use image-specific domain knowledge (these scores and others may be found at http://yann.lecun.com/exdb/mnist/).
	On 20 Newsgroups, hyperopt-sklearn is competitive with similar approaches from the literature (scores taken from~\citet{guan2009class}).
        On Convex Shapes, hyperopt-sklearn outperforms previous automatic algorithm configuration approaches~\citep{eggensperger+etal:2013} and manual tuning~\citep{larochelle+etal:2007}.
    }
    \label{tbl:acc}
    \centering
    \small
    \begin{tabular}{llllll}
        \hline
        \multicolumn{2}{c}{\textbf{MNIST}} & \multicolumn{2}{c}{\textbf{20 Newsgroups}} & \multicolumn{2}{c}{\textbf{Convex Shapes}}  \\
        Approach & Accuracy  & Approach & F-Score & Approach & Accuracy\\
        \hline
        Committee of convnets & 99.8\%                & CFC & 0.928 & \textbf{hyperopt-sklearn} & 88.7\%\\
	\textbf{hyperopt-sklearn} & \textbf{98.7}\%   & hyperopt-sklearn & \textbf{0.856} & hp-dbnet & 84.6\% \\
        libSVM grid search & 98.6\%                   & SVMTorch & 0.848 & dbn-3 & 81.4\%\\
        Boosted trees & 98.5\%                        & LibSVM & 0.843 &  &  \\
    \end{tabular}
    \begin{tablenotes}
      \footnotesize
      \item
	      \textit{In the 20 Newsgroups dataset, the score reported for hyperopt-sklearn is the weighted-average F1 score provided by sklearn. The other approaches shown here use the macro-average F1 score.} 
    \end{tablenotes}
  \end{threeparttable}
\end{table}

>>>>

\begin{table}
  \begin{threeparttable}
    \caption{
        Hyperopt-sklearn scores relative to selections from literature on the three data sets used in our experiments.
        On MNIST, hyperopt-sklearn is one of the best-scoring methods that does not use image-specific domain knowledge (these scores and others may be found at http://yann.lecun.com/exdb/mnist/).
	On 20 Newsgroups, hyperopt-sklearn is competitive with similar approaches from the literature (scores taken from~\citet{guan2009class}).
        On Convex Shapes, hyperopt-sklearn outperforms previous automatic algorithm configuration approaches~\citep{eggensperger+etal:2013} and manual tuning~\citep{larochelle+etal:2007}.
    }
    \label{tbl:acc}
    \centering
    \small
    \begin{tabular}{llllll}
        \hline
        \multicolumn{2}{c}{\textbf{MNIST}} & \multicolumn{2}{c}{\textbf{20 Newsgroups}} & \multicolumn{2}{c}{\textbf{Convex Shapes}}  \\
        Approach & Accuracy  & Approach & F-Score & Approach & Accuracy\\
        \hline
	Committee of convnets & 99.8\%                & CFC & 0.928 & \textbf{hyperopt-sklearn} & \textbf{88.7}\%\\
	\textbf{hyperopt-sklearn} & \textbf{98.7}\%   & \textbf{hyperopt-sklearn} & \textbf{0.856} & hp-dbnet & 84.6\% \\
        libSVM grid search & 98.6\%                   & SVMTorch & 0.848 & dbn-3 & 81.4\%\\
        Boosted trees & 98.5\%                        & LibSVM & 0.843 &  &  \\
    \end{tabular}
    \begin{tablenotes}
      \footnotesize
      \item
	      \textit{In the 20 Newsgroups dataset, the score reported for hyperopt-sklearn is the weighted-average F1 score provided by sklearn. The other approaches shown here use the macro-average F1 score.} 
    \end{tablenotes}
  \end{threeparttable}
\end{table}
